Flexibility of interactions depends on habitat suitability

### 2019-09-06 paper/manuscript.Rmd
Minor edits to intro

Perhaps, because it operates at scales larger than those of the Eltonian niche concept, the abiotic environment is one of the factors that is commonly overlooked by community ecologists when explaining interaction turnover [but see @gravel_bringing_2018]. 
The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition. 
At the heart of biogeography is the idea that the abiotic environment can determine whether a species can have a positive growth-rate when rare in a particular location.
For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the "Grinellian" niche of both species. 
Although less understood, the environment can also affect the interactions, once community composition has been established [@tylianakis_ecological_2017]. 
For instance, some studies show that trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along an elevation/temperature gradient. 
Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress/suitability. 
Previous research is so far equivocal and indicates that environmental stress can have two contrasting effects on species' Eltonian-niche [@tylianakis_ecological_2017].
On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts, they were best adapted to attack.
Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids. 
On the other, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels. 
For instance, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.

We collect available data on plant-pollinator interactions globally and calculate the environmental suitability of all species present at two or more communities to. 
Our main aim is to leverage that information to test the two competing hypotheses that relate environmental stress and Eltionian niche breadth and whether there is a pattern within and across species. 
Specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014]. 
We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to broaden their Eltonian niche. 
Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress. 
Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.

>>>>

Perhaps, because it operates at scales larger than those of the Eltonian niche concept, the abiotic environment is one of the factors that is commonly overlooked by community ecologists when explaining interaction turnover [but see @gravel_bringing_2018]. 
The most evident—and best-studied—way through which the environment can affect the structure of ecological networks is by way of patterns of community composition. 
At the heart of biogeography is the idea that the abiotic environment can determine the "Grinellian" niche of a species, this is whether the species can have a positive growth-rate when rare in a particular location.
For two species to interact, they first need to co-occur in the same community, which can only happen if the environmental conditions of the community fall within the Grinellian niche of both species. 
Although less understood, the environment can also affect the interactions themselves, after community composition has been established [@tylianakis_ecological_2017]. 
For instance, some studies show that trophic interactions, like predation [@mckinnon_lower_2010; @vucic-pestic_warming_2011] and herbivory [@baskett_latitudinal_2018], can increase with temperature but might decrease with precipitation [@pires_predicted_2016], and both plant-plant [@bertness_positive_1994] and plant-pollinator [@tur_evaluating_2016] interactions can switch from facilitative to competitive along an elevation/temperature gradient. 
Contrastingly, other studies have shown either no effect or non-linear effects of temperature or precipitation on plant-pollinator interactions [@devoto_patterns_2005; @gravel_bringing_2018].
One way to summarise the seemingly contradictory evidence of whether the environment can influence whether two species interact or not is by moving from gradients of temperature or precipitation to gradients of environmental stress. 
Previous research is so far equivocal and, taken together, suggest that environmental stress can have two contrasting effects on species' Eltonian-niche [@tylianakis_ecological_2017].
On the one hand, it is possible that when species are under environmental stress, they might be "pressured" to focus on partners with which they are best adapted to interact. 
For instance, @hoiss_altitude_2012 found increased phylogenetic clustering between plants and pollinators at higher altitudes; while @peralta_phylogenetic_2015 found that parasitoids in plantation forest, where environmental stress was higher than in native forests, were constrained to interact with hosts they were best adapted to attack.
Similarly, @lavandero_genotype_2013 found that environmental stress due to higher temperature reduced the breadth of the Eltonian niche of parasitoids. 
On the other, it is also possible that when species are under environmental stress, they are forced to be more flexible in their interactions as higher environmental stress is likely to be reflected in greater energetic or reproductive costs and therefore they might not be able to sustain encounter rates with their preferred partners at sufficient levels. 
In line with this hypothesis, @hoiss_interactive_2015 found that the specialisation of plant-pollinator networks decreased both with elevation and after extreme drought events.
Likewise, @pellissier_spatial_2010 found a positive relationship between niche breadth and environmental stress: disk- or bowl-shaped blossoms (which allow a large number of potential pollinator species to access pollen and nectar rewards) dominated at high altitude flower communities.

We analyse data on plant-pollinator interactions globally and calculate the environmental suitability of all species present at two or more communities to. 
Our main aim is to leverage that information to test the two competing hypotheses that relate environmental stress and Eltionian niche breadth and whether there is a pattern within and across species. 
Specialist species can become "facultative" generalists to reduce their vulnerability to the absence of preferred partners [for example, when variations in climate decouple phenologies; @benadi_specialization_2014]. 
We therefore also expect that as environmental stress increases species with a relatively small number of partners are more likely to broaden their Eltonian niche. 
Species with a large number of partners, on the other hand, should have a larger pool of available partners and might, therefore, be more likely to narrow their niche under environmental stress. 
Importantly, when testing these hypotheses, we control for the potential effects of the environment in community composition and the size of the species fundamental niche, both from an Eltonian (interactions) and Grinellian (environment) perspective.
